

Tool\-Framework is an open source general modular C++ Framework.

\section*{$\ast$\-P\-L\-E\-A\-S\-E N\-O\-T\-E\-: This is the core framework only!!! do not clone this repo for building your own application.}

To create your own Tool\-Framework appliciaion please clone/fork the Tool\-Application repository \href{https://github.com/ToolFramework/ToolApplication}{\tt https\-://github.\-com/\-Tool\-Framework/\-Tool\-Application} which has a script \char`\"{}$\ast$\-Get\-Tool\-Framework.\-sh$\ast$\char`\"{} to pull this repository down as a dependancy and set up everything for you.



 \section*{Concept}





The main executable creates a \hyperlink{classToolChain}{Tool\-Chain} which is an object that holds Tools. Tools are added to the \hyperlink{classToolChain}{Tool\-Chain} and then the \hyperlink{classToolChain}{Tool\-Chain} can be told to Initialise Execute and Finalise each tool in the chain.

The \hyperlink{classToolChain}{Tool\-Chain} also holds a uesr defined \hyperlink{classDataModel}{Data\-Model} which each tool has access too and can read ,update and modify. This is the method by which data is passed between Tools.

User Tools can be generated for use in the tool chain by incuding a \hyperlink{classTool}{Tool} header.

For more information consult the Tool\-Framework manual\-:

\href{https://drive.google.com/file/d/19F-nJpeq3cHJbjV4qiSk5qzpOa7p8keQ}{\tt https\-://drive.\-google.\-com/file/d/19\-F-\/n\-Jpeq3c\-H\-Jbj\-V4qi\-Sk5qzp\-Oa7p8ke\-Q}

or the Doxygen docs

docs \href{https://toolframework.github.io/ToolFrameworkCore/}{\tt https\-://toolframework.\-github.\-io/\-Tool\-Framework\-Core/}

Copyright (c) 2016 Benjamin Richards 